On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-04-05 TTau_Halpha/revision01/response_to_ref.txt

In this paragraph you obtain about 8% of the stellar surface covered
by hot rings. This is quite a large value compared with the values
obtained by Gullbring & Calvet in the papers cited above, which range
rather from 0.1% to 1% for several CTTSs. But this could be due to the
fact that you are using a large Macc rate (10^-7 Msun/yr) for a
CTTS. Does this affect your results ? Was the hot ring surface
coverage recalculated consistently when you computed models with 10^-8
Msun/yr and 10^-9 Msun/yr ? In that case, what values were used ?

   * The surface "area" covered by the hot rings depends only on 
     the geometry of the magnetosphere (Rmi and Rmo); however, 
     the total accretion luminosity (L_acc) depends on the
     mass-accretion rate (Macc).
     The surface intensity of the hot rings is computed according to 
     this total luminosity due to accretion and by assuming they
     radiates as a blackbody.

     If a smaller hot ring surface was adopted, the ring temperature
     will increase in order to have a fixed L_acc for a given amount
     of mass-accretion rate.  So, yes, we calculate the amount of
     total "flux" according to a mass-accretion rate, but the surface
     coverage does not change.

     The level populations are relatively insensitive to the actual 
     distribution of the hot spots on the stellar surface and
     hence, the H-alpha line strength is not affected by the change in
     the area coverage of the rings provided that the change is not too
     greate. If the area coverage is much bigger (e.g. 30%), then the
     geometry of the magnetosphere itself must change significantly.  This
     would result in the line strength slightly for a fixed
     inclination angle, but overall shape of the profile would not
     change so much. For example, we used Rmi=2.2R* and Rmo = 3.0R*
     (Small and Wide (SW) model of Muzerolle et al 2001) which results
     in 8% hot ring coverage. If we were to use Rmi=2.2R* and Rmi =
     2.8R* and Rmo=3.0* (Small and narrow (SN) model of Muzerolle et
     al 2001), then the coverage would be 1% of the total surface,
     which is more similar to the fraction estimated in Gullbring et al
     (2000).  If we look at the model comparison of Muzerolle et al
     (2001) (see their Fig. 5), the line strength changes, but the
     line profiles shape do not change much (except for the 10^3 K
     model). We confirmed, by running additional models, the line
     shapes do not change significantly for H-alpha by changing from
     SW to SN model.

@@

     To make it clear about this point, I have inserted the following
     texts near the end of the 2nd paragraph in  Section 2.1:

        "In our model, the fraction of hot-ring coverage area is
        determined only by the geometry of the magnetosphere (Section
        2.2). Gullbring et al (2000) estimated the fractions of the
        hot-ring coverage area for three intermediate CTTS by using
        the observed UV and optical spectra. They found the range of
        fraction to be 0.3--3.0~per~cent.  This is smaller than the
        value adopted here; however, even if we use 1~per~cent
        hot-ring area coverage model (by changing the width of the
        magnetosphere), we find the line shapes of H$\alpha$ do not
        change significantly (see also figure~5 of Muzerolle et al. 2001). "

@@

     Also I added the following sentence, just before the last
     sentence in Section 2.1:

        "The luminosity ratio and the temperature depend on a adopted
         mass-accretion rate."

Sect. 2.2, 3rd paragraph: You say that the results of Martin (1996)
qualitatively agree with those of Hartmann et al (1994). There is a
comment about that in the Muzerolle et al (1998) (ApJ 492, 743) paper
on page 751, where they also use the Hartmann et al (1994) law. They
say that the Martin (1996) temperature distribution is inadequate to
obtain line emission consistent with the observations, even at Halpha,
while their temperature distribution generates profiles that look like
the observed ones. So I think that you should not say that both
temperatures agree, even qualitatively.  It gives the idea that they
generate the same types of profiles, which is not true. The fact that
they do not agree is actually a big problem, since the Hartmann et
al. (1994) temperature structure, which is somewhat arbitrary,
reproduces the observed profiles, while the Martin (1996) temperature
structure, which was calculated consistently, does not. We are missing
some physics in there.

   * The two temperature structures _do_ agree in a qualitative sense,
     in that their behaviour as a function of distance along a
     streamline follows a similar dependence. Nonetheless, you are
     right that Muzerolle could not reconcile the Martin T structure
     with observations. We have made the following change:

        "Muzerolle et al (1998) found that the line profile models computed
         according to the Martin (1996) temperature structure do not
         agree with observations, unlike profiles based on the (less self-consistent)
         Hartmann et al. (1994) temperature distribution.
	 It is clear that The temperature structure of the magnetosphere is still a large
         source of uncertainty in the accretion model; here  we adopted the model of Hartmann et
         al. (1994). "

@@

Sect. 2.3, 4th paragraph: I could not follow you in the end of the
paragraph. You have p=4*alpha*q and q = -1.15 from Whitney et
al. (2003). You say that in order to be consistent with Krasnopolsky
et al. (2003) who used p = -5/2, the value of alpha was set to
0.76. Well, alpha=p/(4*q)=-2.5/(4*(-1.15))=0.54 and not 0.76.

   * You are absolutely correct. This is a typo, 
     it should be p=-7/2 which is the value used in the models.  
     With p=-7/2,  
         alpha=p/(4*q)=-3.5/(4*(-1.15)) = 0.76.

@@

Sect. 4.1, 6th paragraph I don't understand why the highest
red-shifted line-of-sight velocity is visible only at the high
inclination angles. Looking at Figure 1, at low inclinations (even at
i=0) we actually see all the highest red-shifted material of the upper
right funnel portion (z>0, x>0, for an observer looking from the upper
right corner). Actually, looking at the profiles in Fig. 5, I don't
see much of a change in the redshifted wing width (for example at v >
120 km/s) with the increase in inclination. The blue-shifted wing
changes more.

   * Sorry. I meant to say "the blue-shifted" line-of-sight velocity
     instead of the red-shifted ...  As you mentioned the difference
     in the red wing is very small, but the difference in the blue
     wing is small but visible. By reflecting these points, I have
     made the correction as follows:

       ORIGINAL
       "..., the highest red-shifted line-of-sight velocity is visible
        only at the high inclination angles. This explains the wider
        appearance of the profile with i=80 deg. compared to the
        relatively narrow line appearance of the profile with
        i=10 deg."

       REVISED 
       "..., the highest blue-shifted line-of-sight velocity is seen
        only at the high inclination angles. For example, the
        accretion stream close to the photosphere (~1 R*) above the
        photosphere) on the upper-left quadrant in Fig.1 (x<0 and z>0)
        will be more aligned with the line-of-sight of an observer in
        the upper-right quadrant in the same figure (x>0 and z>0) as
        the inclination increases.  This results in a slight increase
        in the blue wing flux for a higher inclination model as seen
        in Fig. 5."

@@

The last condition is clearly satisfied in all your models, since d is
always less than 173 Rstar. But the inner field lines, passing close
to Rwi, do not satisfy the Blandford & Payne (1982) condition, since
for that you would need to have d < 5.2 Rstar in all cases.

In other words, if you fixed d = 44 Rstar in the disc wind models
presented in the paper, as you say you did in the 4th paragraph of
Sect. 4.2, for the wind to be launched centrifugally according to
Blandford & Payne, the field lines must present Rw > d/tan(60), which
is Rw > 25.4 Rstar. This means that field lines from Rwi = 3 Rstar to
Rw = 25 Rstar will not be able to launch a wind magneto-centrifugally
with d=44 Rstar.

How do you launch the wind in the inner field line region ? If you
cannot launch a wind in that region, how does it affect your results ?

   * I noticed the launching angle (measured from disc plane)
     condition of Blandford & Payne (1982) is not satisfied in the
     inner region of our simple disc wind model.  This is was done so
     that wind has a moderate amount of collimation. Since the stream
     line is straight, the wind will never bend toward the symmetry
     axis (z-axis) as the distance from the disc increases unlike the
     model of Blandford & Payne (1982). We therefore used a larger
     launching angle to simulate the stream lines in the far field (at
     a larger distance from the disc plane) in their model.  This is
     an intrinsic problem with approximating the stream lines with
     straight lines.  Also, in our mode, if
     the launching angle is too small (<60 deg.), the wind absorption
     feature would not been seen for profiles computed with i<60
     deg. since the wind stream line is straight and little material
     is present in the line-of-sight to an observer in this case.
     Since more than 50% of observed H-alpha profiles (e.g. Reipurth
     1996, A&AS, 120, 229 and Alencar & Basri 2000, ApJ 119, 1881) are
     affected by wind absorption, it was necessary for our model to
     used the launching angle (at the inner most part) greater than 60
     degrees to be more consistent with observations.

@@

     If the launching angle (measured from the disc plane) is 60 deg. at
     the inner most part of the  wind, and the inclination angle
     (measured from the symmetry  axis, z-axis) is less than 60 deg., little
     absorption is expected, as demonstrated in Fig. 7.
     The situation will however change if the
     field/stream line is not straight and bending towards the
     symmetry axis as the wind travel higher above the disc.

     In summary, this was necessary compromise in order (1) to be more
     consistent with observation, and (2) to simulate more
     "colliminated" wind (toward the symmetry axis).

     To answer your question how it would effect our results, I ran
     additional models with d=5Rstar which satisfies the wind
     launching condition of Blandford & Payne (1982) in all disc wind
     zone in our model.  These models showed that the wind absorption
     and emission features weakens,  but overall morphology dependence
     of the profiles on the wind temperature and the wind acceleration rate
     is very similar to what we found in the models shown in Figs. 6
     and 9.  Hence, the major conclusions obtained by using the wind
     models with a larger launching angle (at the very inner part of
     the disc) presented in this paper would not differ from the
     conclusions obtained from the disc wind models with d=5Rstar.

     These models (for  Mdot_acc=1x10^-8 Msun/yr & Mdot_wind=1x10^-9
     Msun/yr cases) with d=5Rstar are posted on the following website.

     http://www.astro.ex.ac.uk/people/rk/profiles/extra2

@@

     To clarify the points you raised above, I have inserted the
     following in text (mostly the same as mentioned above).

     After the 4th paragraph in Section 4.3, the following new
     paragraphs are inserted:

       "Blandford & Payne (1982) showed that in order to launch a wind
        from a disc plane magneto-centrifugally, the launching angle
        (theta_L, measured from the equatorial disc plane) must be
        less than 60 degrees. In our models, the wind launching zone
        is restricted in between Rwi < wi < Rwo (see Fig. 1 and Table
        1) with Rwi = 3 Rstar and Rwo=1 au.  This sets the upper limit
        of the source displacement distance (d) to be around 5.2 Rstar
        if we want to satisfy the launching angle condition of
        Blandford & Payne (1982) for all the stream lines in our disc
        wind model.  In the models presented in Fig. 6 (and later in
        Fig. 9 in next section), we have adopted d =22 Rstar
        instead. We have used this larger source
	displacement distance for the following two reasons: (1) to
	simulate a more 'colliminated' wind (toward the symmetry axis,
	and (2) for greater consistency with the fraction of H-alpha
	profiles affected by wind absorption in observations (ref xxxxx).

      	Since the stream lines in our simple disc wind are represented
	by straight lines, the wind never bends toward the symmetry
	axis (z-axis) as the distance from the disc increases unlike
	the model of Blandford & Payne (1982). We therefore used a
	larger launching angle to simulate the stream lines in the far
	field (at a larger distance from the disc plane) in their
	model.  This is an intrinsic problem with approximating the
	stream lines with straight lines.  Also, in
	our mode, if the launching angle is too small (<60 deg.), the
	wind absorption feature would be not been seen or would be
	very small for profiles computed with i<60 deg.  If the
	launching angle is 60 deg. at the inner most part of the wind,
	and the inclination angle (measured from the symmetry axis,
	z-axis) is less than 60 deg., little (wind) absorption is
	expected, as demonstrated in Figure 7.  The situation will
	however changes if the field/stream line is not straight and
	bending towards the symmetry axis as the wind travel higher
	above the disc.  Since more than 50 per cent of observed
	H-alpha profiles (e.g. Reipurth 1996, A&AS, 120, 229 and
	Alencar & Basri 2000, ApJ 119, 1881) are affected by wind
	absorption, it was necessary for our model to used the
	launching angle (at the inner most part) greater than 60
	degrees to be more consistent with observations; although this
	would mean that the launching angle condition of Blandford and
	Payne (1982) is violated for wind from a very inner part of
	the disc.

	 In addition to the models given in Figs. 6 and 9, we have
	 computed the models with d=5Rstar (not shown here) which
	 satisfies the wind launching condition of Blandford & Payne
	 (1982) in all parts of the disc wind zone in our model.
	 These models showed that the wind absorption and emission
	 features weaken, but overall morphology dependence of the
	 profiles on the wind temperature rate and the wind
	 acceleration rate are similar to the models
	 shown in Figs. 6 and 9.  The minimum inclination angle at
	 which the wind absorption becomes important is larger than
	 that of the models with a larger source displacement (d = 22
	 Rstar) as expected."

@@

Sect. 4.3, 5th paragraph: It is hard to see in Fig. 10 that the
position of minimum flux in the absorption moves blue-ward. I actually
don not see any difference between the models with mu=0.1 and 0.2.

   * You are correct.
     I rephrase the sentence as follows

     ORIGINAL 
     "The figure shows that as $\mu$ increases the
     P-Cygni absorption deepens only slightly, and the position of minimum
     flux in the absorption trough appears to move blue-ward."

     REVISED
     "The figure shows that as $\mu$ increases the
     P-Cygni absorption deepens only slightly  and the position of minimum
     flux in the absorption trough appears to remain at same location."

@@

     for the profile computed at i=10,55,80 and for beta=0.2, 0.5,
     1.0, 2.0 Twind=7000, 8000, 9000, 10000K

      According to these models which use a more typical
      mass-accretion rate, Type III-B can be seen for at least in
      three models with fast accelerating and high wind temperature
      i.e. (beta, Twind) = (0.2, 10000K), (0.5, 9000K) and (0.5,
      10000K).

      I added a following comments based on these additional runs.

      "Although Type III-B profiles do not occur at macc=10^-8, we
      have examined the intermediate case of macc=3x10-8, which may
      represent a typical T Tauri mass accretion rate  (Gullbring et
      al. 1998; Calvet et al. 2004). We find that the models with fast accelerating,
      high temperature winds do display  Type III-B profiles. It is
      clear that our model, as it stands, requires above-average (but
      perhaps not atypical) mass-accretion rates in order to produce
      Type III-B profiles. It is less clear whether the 14 Type-IIIB
      objects found by Reipurth et al. consistute the highest
      mass-accretors in their sample: the aveage EW for T~Tauri stars
      with Type III-B profiles is 69\AA, which is in the top quartile
      of their complete T~Tauri star sample, perhaps indicating that
      Type-IIIB profiles are associated with high EWs, and therefore
      strong mass-accretion."

@@

   * Yes, you are quite right. I am aware of the effect of the
     inclined magneto-axis CTTS models. In fact, I wrote a paper on SU
     Aur Pa-beta line variability. H-alpha variability of of SU Aur
     indeed shows a very complex line profile morphology dramatically
     changing with its rotational phase (e.g.  Johns & Basri 1995, see
     also their movie
     http://sprg.ssl.berkeley.edu/~cmj/html/suaur.mpg).  Although it
     does not look it has a clear IV-R type profile at any given
     rotational phase for H-alpha, I am aware that Pa-beta line does
     show IV-R type profile, and the strength of inverse P-Cyg or the
     absorption features in the redwing changes as the rotational
     phase changes (e.g. Kuorsawa et al, 2005, MNRAS, 358, 671).

     I wanted to restrict the cases for purely axi-symmetric
     geometries in this paper for clarity of discussion.  In reality,
     a situation may not be as simple as this classification, as we
     know the lines are sometimes highly variable. This problem will
     be tackled in near future. For a starter, I am currently
     computing line profiles based on the MHD model of Romanova et al
     (2003, ApJ, 595, 1009) who considered the disc accretion problem
     with an inclined dipole magnetic field, and investigate if the
     overall line variability features seen in the observation can be
     explained by this model. I am working on the case with and
     without the additional outflow (discwind or/and stellar wind).

     I will clarify this point by adding the following near the end of
     the first paragraph in Section 5.1 :

       "Although in general H-alpha in the spectra of CTTS shows a
        significant amount of variablity, which may in some cases
        induced by the rotational motion of an inclined magnetosphere
        (e.g. Johns &  Basri 1995; Bouvier et al. 2003), we restrict
        our discussion in this section to the axisymmetric case only."

@@

    Also a short comment is added at the end of Type IV-R section,

       "The restriction in the inclination angle mentioned above would
        be relaxed if the axis of the magnetosphere was tilted with
        respect to the rotational axis, since the line-of-sight from an
        observer to the hot rings will pass through 
        different parts of the magnetosphere as the rotational phase
        changes."

@@

Sect. 5.2, 3rd paragraph: What is the mass loss rate used in the
stellar wind models ? This value should be added to the text. Matt &
Pudritz (2005) suggest 10^-9 Msun/yr to solve the angular momentum
problem.

   * Thank you for pointing this out.  I should have quoted the
     mass-loss rate used in the models.    
     In both models in Fig.13, Mdot_wind = 10^-8 Msun/yr is used so 
     that mu=Mdot_wind/Mdot_acc = 0.1, and to be consistent with 
     the mass-accretion rate (Mdot_acc=10^-7 Msun/yr) used for the
     models in earlier in the paper. It seems that the ratio mu is an
     important factor in Matt & Pudritz (2005) in balancing the
     torques on a central star (their equation 3).
     I tried the models with Mdot_wind = 10^-9 Msun/yr  (keeping
     mu=0.1), and found the same inclination dependency for these
     models, so the main conclusion of this section 
     does not change when Mdot_wind is changed from 10^-8 Msun/yr to
     10^-9 Msun/yr.

@@

     To reflect your points, I added the following in the text 
     (Sect. 5.2, 4th paragraph).

     After the first sentence of the paragraph, I inserted:

        "The mass-loss rate of the stellar wind in this model is 10^-8
	Msun/yr, which is same as the mass-loss rate used in the
	disc-wind magnetosphere hybrid model in the same figure.  In
	both models, the mass-accretion rate of 10^-7 Msun/yr is
	used."

     At the end of the paragraph, I inserted: 
        "A similar inclination dependency of EW is found for lower
        mass-loss rate models (e.g. Mdot_wind = 10^-9 Msun/yr)
        while keeping mu=0.1."

### 2006-04-05 TTau_Halpha/revision01/response_to_ref.txt

     Also in the figure caption of Figure 13  just before the last
	sentence,  I added:
	"The wind mass-loss rates used in both models is Mdot_wind =
	10^-8 Msun/yr."

### 2006-04-05 TTau_Halpha/revision01/kurosawa.tex
Corrections discussed with Tim have made to this version.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@696 25464f21-6099-402c-b30a-640f1d40d38b

In the currently favoured model of accretion in CTTS, the accretion
disc is disrupted by the magnetosphere, which channels the gas from
the disc onto the stellar surface (e.g., \citealt{uchida:1985};
\citealt{koenigl:1991}; \citealt{cameron:1993};
\citealt{shu:1994}). This picture is supported by recent measurements
of strong ($\sim 10^{3}\mathrm{G}$) magnetic fields in CTTS (e.g.,
\citealt{johns-krull:1999}; \citealt{symington:2005b}) and by
radiative transfer models which reproduce the gross characteristics of
observed profiles for some CTTS (\citealt*{muzerolle:2001}). In
particular the magnetospheric accretion (MA) model explains blue-ward
asymmetric emission line profiles as resulting from the partial
occultation of the flow  by the inner part of the accretion disc and
by the stellar photosphere, while inverse 
P~Cygni profiles in the MA model result from inflowing material at
near free-fall velocities seen projected against hotspots on the
stellar surface.

@@

An additional continuum source is considered for models which include 
magnetospheric accretion: as the infalling gas approaches the stellar
surface, it decelerates in a strong shock, and is heated to $\sim
10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
be absorbed by the gas locally, and re-emitted as optical and UV
(\citealt{calvet:1998}; \citealt{gullbring:2000}). This
will create hot rings where the magnetic field intersects with the
surface. We assume that the free-falling kinetic energy is thermalized
in the radiating layer, and is re-emitted as blackbody radiation with
a single temperature. With the parameters of the magnetosphere and the
star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
of the surface is covered by the hot rings. 
In our model, the fraction of hot-ring coverage area is
determined only by the geometry of the magnetosphere
(Section~\ref{sub:Magnetosphere}). \citet{gullbring:2000} estimated the
fractions of the hot-ring coverage area for three intermediate CTTS by
using the observed UV and optical spectra. They found the range of
fraction to be 0.3--3.0~per~cent.  This is smaller than the value adopted
here; however, even if we use 1~per~cent hot-ring area
coverage model (by changing the width of the magnetosphere), we
find the line shapes of H$\alpha$ do not change significantly.

@@

\caption{Summary of the reference classical T~Tauri star model
  parameters. Note that a typical mass-accretion rate of CTTS is $\sim 3
  \times 10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
  (e.g. \citealt{gullbring:1998}; \citealt{calvet:2004}); however, a
  slightly higher mass-accretion rate is adopted here to demonstrate the 
  effect of line-broadenings more clearly (c.f. Section~\ref{sub:model-acc}). }
\label{tab:std_parameters}

@@

The temperature structure of the magnetospheric used by
\citet{hartmann:1994} is adopted here. They computed the temperature,
assuming a volumetric heating rate which is proportional to $r^{-3}$,
by solving the energy balance of the radiative cooling rate of
\citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
\citet{martin:1996} presented a self-consistent determination of the
thermal structure of the inflowing gas along the dipole magnetic field
(equation~\ref{eq:dipole}) by solving the heat equation coupled to the
rate equations for hydrogen. He found that main heat source is
adiabatic compression due to the converging nature of the flow, and
the major contributors to the cooling process are bremsstrahlung
radiation and line emission from Ca~II and Mg~II ions. 
Although the model of \citet{martin:1996} seems to be more comprehensive
than that of \citet{hartmann:1994}, \citet*{muzerolle:1998} found that
the line profile models computed according to the temperature
structure of the former do not agree with observations while they do
have much better agreement when the temperature of the latter model was
used.  The temperature structure of the magnetosphere is still a big
uncertainty in the accretion model; however, for a heuristic reason,
we adopted the model of \citet{hartmann:1994}.

@@

\citet{blandford:1982} showed that in order to launch a wind from a
disc plane magneto-centrifugally, the launching angle ($\theta_{L}$,
measured from the equatorial disc plane) must be less than $60^{\circ}$.
 In our models, the wind launching zone is restricted in
between $R_{\mathrm{wi}} < w_{i} < R_{\mathrm{wo}}$ (see
Fig.~\ref{fig:config_discwind} and Table~\ref{tab:std_parameters}) with
$R_{\mathrm{wi}} = 3\,R_{*} $ and 
$R_{\mathrm{wo}}=1$~au.  This sets the upper limit of the source displacement
distance ($d$) to be around $5.2\,R_{*}$ if we want to satisfy the
launching angle condition of \citet{blandford:1982} for all the
stream lines in our disc wind model.  In the models presented in
Fig.~\ref{fig:atlas_discwind_only} (and later in
Fig.~\ref{fig:atlas_hybrid} in next section), we have adopted 
$d =22\, R_{*}$ instead. This means that some part of the disc
wind ($3\,R_{*} < w_{i} < 25.4\,R_{*}$) may not be able to be launched
from the disc plane according to the model of \citet{blandford:1982}.
We have used a larger launching angle or a larger source displacement
distance for the following two reasons: (1)~to simulate more
\emph{collimated} wind (toward the symmetry axis, and (2)~to be more
consistent with the fraction of H$\alpha$ profiles affected by wind
absorptions in observations.

Since the stream lines in our simple disc wind are represented by
straight lines, the wind never bends toward the symmetry axis ($z$-axis)
as the distance from the disc increases unlike the
model of \citet{blandford:1982}. We therefore used a larger
launching angle to simulate the stream lines in the far field (at a larger
distance from the disc plane) in their model.  This is an intrinsic
problem with approximating the stream lines with straight lines. A
better model is perhaps to compute the field lines using
\citet{blandford:1982} model as done so in \citet{alencar:2005}.
Also, in our mode, if the launching angle is too small
($<60^{\circ}$), the wind absorption feature would be not been seen
or would be 
very small for profiles computed with an inclination angle
$i<60^{\circ}$.  If the launching angle is $60^{\circ}$ at the inner
most part of the wind, and the inclination 
angle (measured from the symmetry axis, $z$-axis) is less than $60^{\circ}$,
little (wind) absorption is expected, as demonstrated in Fig.~\ref{fig:discwind_d_effect}.
The situation will however change if the field/stream lines are not
straight and bending towards the symmetry axis as the wind travel
higher above the disc.  Since more than 50~per~cent of observed
H$\alpha$ profiles (e.g. \citealt{reipurth:1996};
\citealt{alencar:2000}) are affected by wind absorption, it was 
necessary for our model to used the launching angle (at the inner most
part) greater than $60^{\circ}$ to be more consistent with observations;
although this would mean that the launching angle condition of
\citet{blandford:1982} is violated for wind from a very inner part
of the disc.

In addition to the models given in Figs.~\ref{fig:atlas_discwind_only}
and \ref{fig:atlas_hybrid}, we have computed the models with $d = 5\,
R_{*}$ (not shown here) which satisfies the wind launching condition
of \citet{blandford:1982} in all parts of the disc wind zone in our model.  These
models showed that the wind absorption and emission features weaken,
but overall morphology dependence of the profiles on the wind
temperature rate and the wind acceleration rate is similar to what we
found in the models shown in Figs.~\ref{fig:atlas_discwind_only} and
\ref{fig:atlas_hybrid}.  The minimum inclination angle at which the
wind absorption becomes important is larger than that of the models
with a larger source displacement ($d = 22\, R_{*}$) as expected.

@@

The effect of changing the ratio of the wind mass-loss rate to
mass-accretion rate
($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
in Fig.~\ref{fig:discwind_mu_effect}. With a fixed value of
mass-accretion rate
($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
mass-loss rate is varied. The figure shows that as $\mu$ increases the
P-Cygni absorption deepens only slightly, and the position of minimum
flux in the absorption trough appears to remain at same positions.  On the other
hand, the flux peak increases and the line wings become stronger as
$\mu$ increases.  Although MHD models suggest
(e.g.~\citealt{koenigl:2000}) that $\mu \sim 0.1$, the figure suggest
that models with a relatively wide range of $\mu$ (e.g.~between 0.05 and
0.2 in this case) produce profiles similar to observations.

>>>>

In the currently favoured model of accretion in CTTS, the accretion
disc is disrupted by the magnetosphere, which channels the gas from
the disc onto the stellar surface (e.g., \citealt{uchida:1985};
\citealt{koenigl:1991}; \citealt{cameron:1993};
\citealt{shu:1994}). This picture is supported by recent measurements
of strong ($\sim 10^{3}\mathrm{G}$) magnetic fields in CTTS (e.g.,
\citealt{johns-krull:1999}; \citealt{symington:2005b}) and by
radiative transfer models which reproduce the gross characteristics of
observed profiles for some CTTS (\citealt*{muzerolle:2001}). In
particular the magnetospheric accretion (MA) model explains blue-ward
asymmetric emission line profiles as resulting from the partial
occultation of the flow by the stellar photosphere and by the inner
part of the accretion disc, while inverse 
P~Cygni profiles in the MA model result from inflowing material at
near free-fall velocities seen projected against hotspots on the
stellar surface.

@@

An additional continuum source is considered for models which include 
magnetospheric accretion: as the infalling gas approaches the stellar
surface, it decelerates in a strong shock, and is heated to $\sim
10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
be absorbed by the gas locally, and re-emitted as optical and UV
(\citealt{calvet:1998}; \citealt{gullbring:2000}). This
will create hot rings where the magnetic field intersects with the
surface. We assume that the free-falling kinetic energy is thermalized
in the radiating layer, and is re-emitted as blackbody radiation with
a single temperature. With the parameters of the magnetosphere and the
star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
of the surface is covered by the hot rings. 
In our model, the fraction of hot-ring coverage area is
determined only by the geometry of the magnetosphere
(Section~\ref{sub:Magnetosphere}). \citet{gullbring:2000} estimated the
fractions of the hot-ring coverage area for three intermediate CTTS by
using the observed UV and optical spectra. They found the range of
fraction to be 0.3--3.0~per~cent.  This is smaller than the value adopted
here; however, even if we use 1~per~cent hot-ring area
coverage model (by changing the width of the magnetosphere), we
find the line shapes of H$\alpha$ do not change significantly (see
also Fig.~5 of \citealt{muzerolle:2001}).

@@

\caption{Summary of the reference classical T~Tauri star model
  parameters. Note that a typical mass-accretion rate of CTTS is $\sim 3
  \times 10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
  (e.g. \citealt{gullbring:1998}; \citealt{calvet:2004}); however, a
  slightly higher mass-accretion rate is adopted here to demonstrate the 
  effect of line-broadening more clearly (c.f. Section~\ref{sub:model-acc}). }
\label{tab:std_parameters}

@@

The temperature structure of the magnetospheric used by
\citet{hartmann:1994} is adopted here. They computed the temperature,
assuming a volumetric heating rate which is proportional to $r^{-3}$,
by solving the energy balance of the radiative cooling rate of
\citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
\citet{martin:1996} presented a self-consistent determination of the
thermal structure of the inflowing gas along the dipole magnetic field
(equation~\ref{eq:dipole}) by solving the heat equation coupled to the
rate equations for hydrogen. He found that main heat source is
adiabatic compression due to the converging nature of the flow, and
the major contributors to the cooling process are bremsstrahlung
radiation and line emission from Ca~II and Mg~II ions. 
\citet*{muzerolle:1998} found that the line profile models computed
according to the temperature structure of \citet{martin:1996} do not
agree with observations, unlike profiles based on the (less
self-consistent) \citet{hartmann:1994} temperature distribution.  It
is clear that The temperature structure of the magnetosphere is still
a large source of uncertainty in the accretion model; here we adopted
the model of \citet{hartmann:1994}.

@@

\citet{blandford:1982} showed that in order to launch a wind from a
disc plane magneto-centrifugally, the launching angle ($\theta_{L}$,
measured from the equatorial disc plane) must be less than $60^{\circ}$.
 In our models, the wind launching zone is restricted in
between $R_{\mathrm{wi}} < w_{i} < R_{\mathrm{wo}}$ (see
Fig.~\ref{fig:config_discwind} and Table~\ref{tab:std_parameters}) with
$R_{\mathrm{wi}} = 3\,R_{*} $ and 
$R_{\mathrm{wo}}=1$~au.  This sets the upper limit of the source displacement
distance ($d$) to be around $5.2\,R_{*}$ if we want to satisfy the
launching angle condition of \citet{blandford:1982} for all the
stream lines in our disc wind model.  In the models presented in
Fig.~\ref{fig:atlas_discwind_only} (and later in
Fig.~\ref{fig:atlas_hybrid} in next section), we have adopted 
$d =22\, R_{*}$ instead. This means that some part of the disc
wind ($3\,R_{*} < w_{i} < 25.4\,R_{*}$) may not be able to be launched
from the disc plane according to the model of \citet{blandford:1982}.
We have used a larger launching angle or a larger source displacement
distance for the following two reasons.

First, we want to simulate a more \emph{colliminated} wind (toward
the symmetry axis).  Since the stream lines in our simple disc
wind are represented by straight lines, the wind never bends
toward the symmetry axis ($z$-axis) as the distance from the
disc increases unlike the model of \citet{blandford:1982}. We
therefore used a larger launching angle to simulate 
the stream lines in the far field (at a larger distance from
the disc plane) in their model.  This is an intrinsic problem
with approximating the stream lines with straight lines.

Second, the larger source displacement model would provide a greater
consistency with the fraction of H$\alpha$ profiles affected by wind
absorption seen in observations.  According to the observations of
\citet{reipurth:1996} and \citet{alencar:2000}, more than 50 per cent
of CTTS show wind absorption features in their H$\alpha$
profiles. In our model, if the launching angle is too small
($\theta_{\mathrm{L}}<60^{\circ}$), the wind absorption feature would not be seen or
would be very small for profiles computed with $i<60^{\circ}$, as
demonstrated in Fig.~~\ref{fig:discwind_d_effect}.  The situation will
however change if the field/stream line is not straight and bending
towards the symmetry axis as the wind travel higher above the disc.

In addition to the models given in Figs.~\ref{fig:atlas_discwind_only}
and \ref{fig:atlas_hybrid}, we have computed the models with $d = 5\,
R_{*}$ (not shown here) which satisfies the wind launching condition
of \citet{blandford:1982} in all parts of the disc wind zone in our
model.  These models showed that the wind absorption and emission
features weaken, but overall morphology dependence of the profiles on
the wind temperature and the wind acceleration rate is similar to
what we found in the models shown in
Figs.~\ref{fig:atlas_discwind_only} and \ref{fig:atlas_hybrid}.  The
minimum inclination angle at which the wind absorption becomes
important is larger than that of the models with a larger source
displacement ($d = 22\, R_{*}$) as expected.

@@

The effect of changing the ratio of the wind mass-loss rate to
mass-accretion rate
($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
in Fig.~\ref{fig:discwind_mu_effect}. With a fixed value of
mass-accretion rate
($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
mass-loss rate is varied. The figure shows that as $\mu$ increases the
P-Cygni absorption deepens only slightly, and the position of minimum
flux in the absorption trough appears to remain at same location.  On the other
hand, the flux peak increases and the line wings become stronger as
$\mu$ increases.  Although MHD models suggest
(e.g.~\citealt{koenigl:2000}) that $\mu \sim 0.1$, the figure suggest
that models with a relatively wide range of $\mu$ (e.g.~between 0.05 and
0.2 in this case) produce profiles similar to observations.
